Applying Analytic Hierarchy Process to Industrial Process Design in a Nuclear Renewable Hybrid Energy System

### 2021-06-23 manuscript/document-package/references/references.tex

\usepackage[singlelinecheck=false]{caption}
\captionsetup[table]{skip=7pt,labelsep=period} %sets a space after table caption
\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format

@@

\makeatletter
\newcommand*\ftp{\fontsize{16.5}{17.5}\selectfont}
\makeatother

@@

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
\lhead{\scriptsize }
\chead{\scriptsize \textit{ - Draft Manuscript}}
\rhead{\scriptsize \today}
\rfoot{\thepage}

\begin{filecontents}{references.bib} 
\end{filecontents}

%\newacronym{}{}{}

@@

\begin{titlepage}
    \title{}
    \author{
        , 
        , 
        \textsuperscript{*}
        \\ \\ \\
        \\

        \\ \\ \\
        \textsuperscript{*}
    }
\clearpage %not have page number on title page
\maketitle
\vspace*{\fill}
\begin{flushright}{
        \noindent Number of pages - \pageref{LastPage} \\
        \noindent Number of tables - \totaltables \\
        \noindent Number of figures - \totalfigures 
}
\end{flushright}
\thispagestyle{empty} %start with page number 1 on second page
\end{titlepage}

@@

\section*{Abstract}

\newpage

\printnoidxglossary

\newpage

\section{Introduction} \label{sec-intro}

\subsection{Motivation} \label{sec-motiv}

\subsection{Goals} \label{sec-goals}

\begin{enumerate}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
    \item 
    \item  
    \item 
\end{enumerate}

\newpage

\section{Background} \label{sec-bak}

\newpage

\section{Theory} \label{sec-theo}

\newpage

\section{Methodology} \label{sec-meth}

\newpage

\section{Results} \label{sec-res}
\subsection{Objective} \label{sec-obj}

\newpage

\section{Discussion} \label{sec-disc}

\newpage

\section{Future work} \label{sec-fwk}

\newpage

\section{Summary remarks} \label{sec-sum}

Major results and implications include - 
\begin{itemize}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex]
    \item
    \item
    \item
\end{itemize}

\newpage

\section*{Acknowledgements}

\newpage

@@

\newpage

\section*{Tables}

{%
\let\oldnumberline\numberline%
\renewcommand{\numberline}{\tablename~\oldnumberline}%
\listoftables%
}

\newpage

%\begin{table}[h!]
%    \centering
%    \caption{Title}
%        \begin{tabular}{|c|c|c|c|}
%            \hline
%            A&
%            B&
%            C&
%            D
%            \\
%            \hline
%            X
%            &X
%            &X
%            &X
%            \\
%            \hline
%        \end{tabular}
%    \label{tab-label}
%\end{table}

\newpage

%\begin{spacing}{1}
%\begin{longtable}{|c|c|c|c|c|}
%    \caption{Title}
%    \label{tab-label-name} \\
%    \hline
%    \multicolumn{1}{|c|}{A}&
%    \multicolumn{1}{c|}{B}&
%    \multicolumn{1}{c|}{C}&
%    \multicolumn{1}{c|}{D}&
%    \multicolumn{1}{c|}{E}
%    \\
%    \hline
%    \endfirsthead
%    \multicolumn{5}{c}{{\tablename\ \thetable{} - continued}} \\
%    \hline
%    \multicolumn{1}{|c|}{A}&
%    \multicolumn{1}{c|}{B}&
%    \multicolumn{1}{c|}{C}&
%    \multicolumn{1}{c|}{D}&
%    \multicolumn{1}{c|}{E}
%    \\
%    \hline
%    \endhead
%    \hline
%    \endfoot
%    \hline
%    \endlastfoot
%    X
%    &X
%    &X
%    &X
%    &X
%    \\
%    \hline
%\end{longtable}
%\end{spacing}

\newpage

\section*{Figures}

{%
\let\oldnumberline\numberline%
\renewcommand{\numberline}{\figurename~\oldnumberline}%
\listoffigures%
}

\newpage

%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.X\textwidth]{.png}
%    \caption{}
%    \label{fig-label-name}
%\end{figure}

\newpage

%\appendix

%\begin{appendices}

%\renewcommand{\thesection}{\Roman{section}}

%\section{} \label{}

%\end{appendices}

>>>>

\usepackage[singlelinecheck=false]{caption}
\captionsetup[table]{skip=7pti,labelsep=period} %sets a space after table caption
\captionsetup[figure]{skip=7pt,labelformat={default},labelsep=period} %sets space above caption, 'figure' format

@@

@@

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
\lhead{\scriptsize }
\chead{\scriptsize \textit{- Draft Manuscript}}
\rhead{\scriptsize \today}
\rfoot{\thepage}

@@

\begin{titlepage}
    \title{Applying Analytic Hierarchy Process to Industrial Process Design in a Nuclear Renewable Hybrid Energy System}
    \author{
        , 
        , 
        \textsuperscript{*}
        \\ \\ \\
        \\

        \\ \\ \\
        \textsuperscript{*}
    }
\clearpage %not have page number on title page
\maketitle

\thispagestyle{empty} %start with page number 1 on second page
\end{titlepage}

@@

\nocite{*}

@@
